\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-06 paper.qmd
Updated MNIST section
Added missing reference for MNIST

In the field of single-cell studies, a common analytical task involves clustering to identify groups of cells with similar expression profiles. NLDR methods are commonly used to display clusters, and help to verify the results. For example, @chen2023 illustrates the use of UMAP to identify clusters in Human Peripheral Blood Mononuclear Cells (PBMC3k). There are $2622$ single cells. First 9 principal components are used to generate the UMAP. @fig-NLDR-variety (a) is the reproduction of the published plot.

@@

The digit 1 of the MNIST dataset consists of $7877$ grayscale images of handwritten digits [@lecun2010]. Before further analysis, PCA was used to preprocess the data, where the first $10$ principal components, explaining 83% of the total variation, were selected. The objective is to select a reasonable \gD{} layout, representing the non-linear structure of the digit 1 dataset in $10\text{-}D$.

>>>>

In the field of single-cell studies, a common analytical task involves clustering to identify groups of cells with similar expression profiles. NLDR methods are commonly used to display clusters, and help to verify the results. For example, @chen2023 illustrates the use of UMAP to identify clusters in Human Peripheral Blood Mononuclear Cells (PBMC3k). There are $2622$ single cells. First 9 principal components are used to generate the UMAP. @fig-NLDR-variety (a) is the reproduction of the published plot. The objective is to select a reasonable UMAP layout, representing the non-linear structure of the digit 1 dataset in $10\text{-}D$.

@@

The digit 1 of the MNIST dataset consists of $7877$ grayscale images of handwritten digits [@lecun2010]. Before further analysis, PCA was used to preprocess the data, where the first $10$ principal components, explaining 83% of the total variation, were selected. The objective is to select a reasonable \gD{} layout, representing the non-linear structure of the digit 1 dataset in $10\text{-}D$ (@fig-mnist-tri-proj (a)).

### 2024-09-06 paper.tex
Updated MNIST section
Added missing reference for MNIST

In the field of single-cell studies, a common analytical task involves
clustering to identify groups of cells with similar expression profiles.
NLDR methods are commonly used to display clusters, and help to verify
the results. For example, \citet{chen2023} illustrates the use of UMAP
to identify clusters in Human Peripheral Blood Mononuclear Cells
(PBMC3k). There are \(2622\) single cells. First 9 principal components
are used to generate the UMAP. Figure~\ref{fig-NLDR-variety} (a) is the
reproduction of the published plot.

@@

The digit 1 of the MNIST dataset consists of \(7877\) grayscale images
of handwritten digits \citep{lecun2010}. Before further analysis, PCA
was used to preprocess the data, where the first \(10\) principal
components, explaining 83\% of the total variation, were selected. The
objective is to select a reasonable \gD{} layout, representing the
non-linear structure of the digit 1 dataset in \(10\text{-}D\).

>>>>

In the field of single-cell studies, a common analytical task involves
clustering to identify groups of cells with similar expression profiles.
NLDR methods are commonly used to display clusters, and help to verify
the results. For example, \citet{chen2023} illustrates the use of UMAP
to identify clusters in Human Peripheral Blood Mononuclear Cells
(PBMC3k). There are \(2622\) single cells. First 9 principal components
are used to generate the UMAP. Figure~\ref{fig-NLDR-variety} (a) is the
reproduction of the published plot. The objective is to select a
reasonable UMAP layout, representing the non-linear structure of the
digit 1 dataset in \(10\text{-}D\).

@@

The digit 1 of the MNIST dataset consists of \(7877\) grayscale images
of handwritten digits \citep{lecun2010}. Before further analysis, PCA
was used to preprocess the data, where the first \(10\) principal
components, explaining 83\% of the total variation, were selected. The
objective is to select a reasonable \gD{} layout, representing the
non-linear structure of the digit 1 dataset in \(10\text{-}D\)
(Figure~\ref{fig-mnist-tri-proj} (a)).
